An New Search for Supernova Remnants in NGC\,6946

### 2019-01-08 ms.tex
Updates from ShareLaTeX

\todo[inline]{For the Overview Figure, ksl and wpb like the version that shows the galaxy light (currently Fig. 2).  Frank is responsible for updating the overview figures, and describing them in the text.  Bill is responsible for one or more snap shot  region figures to show what objects we select. Then in addition to the overview figure, we should show an enlargement of a smaller region in a multi-panel format, showing the subtracted data.  He is also responsible for the associated text. .}

To select SNR candidates, we used the DS9 display program to show the continuum-subtracted WIYN images in all three emission lines, as well as \sii:\ha\  and \oiii:\ha\ ratio images, and a continuum image (to distinguish stars  or stellar subtraction residuals from point-like nebulae).   We then visually inspected these to select SNR candidates based on a high  \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) conducted independent inspections, and then we conferred to agree on a consensus list of 147 candidates, including the 27 from MF97.   In addition, we selected 51 objects with relatively high \oiii:\ha\ ratios, in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy. With ten SNe in the last century, one might expect a number of young, ejecta-dominated SNRs to be present.  Though none of the O-selected candidates had ratios as extreme as seen for Cas A or 1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.  Finally, we inspected the positions of the nine\footnote{As of the 2011 observations there were nine SNe; a tenth SN was recorded in 2017.} historical SNe in \gal\ for evidence of nebular emission, and detected line emission only at the positions of SN1980K and SN2004et, both of which we targeted for follow-up spectra.

\todo[inline]{ksl - It might be worthwhile to have a few sentences of comparison here to our work on M83 where the Magellen seeing made if far easier to see extended emission, and in M33 of course where all of the SNRs are resolved.  This is about the limit of what we can do from the ground, particularly with the seeing we had with WYIN.  To do better, one needs better seeing.}

@@

\todo[inline]{We need a consistent story about the HII regions.  We mention that we selected some O3 objects.  We got spectra of 24 of these.   We have another 41 spectra of HII regions along the slit.  We got very few HII regions just by chance, though these are included in the 41.  It's hard to actually parse out the history of which are which.}

@@

\begin{figure}
\plotone{fig_example_spectra.pdf}
\caption{Examples of the spectra obtained for three representative SNR candidates and one H II region.  The three SNR spectra were selected to illustrate the quality of the spectra for a bright, medium bright and fairly faint candidate.  \label{fig_example_spectra}}
\end{figure}

@@

\begin{figure}
\plottwo{fig_n2_ha_gc.pdf}{fig_s2_ha_gc.pdf}
\caption{Line ratios of [N II]:\ha\ and [S II]:\ha\ as a function of GCD.  Both SNR candidates and HII regions are shown.     \label{fig_metal_ratios}}

>>>>

\todo[inline]{For the Overview Figure, ksl and wpb like the version that shows the galaxy light (currently Fig. 2).  Frank is responsible for updating the overview figures, and describing them in the text.}

%\todo[inline]{Bill is responsible for one or more enlargements of a smaller region in a multi-panel format, showing the subtracted data.  He is also responsible for the associated text.  WPB: Both of these (figure and text) have been done in the section below.}

To select SNR candidates, we used the DS9 display program to show the continuum-subtracted WIYN images in all three emission lines as well as a \sii:\ha\ ratio image and a continuum image (to discriminate stars or stellar subtraction residuals from point-like nebulae).   We then visually inspected these to select SNR candidates based on a high \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) compiled independent candidate lists; we then conferred to agree on a consensus list of 147 candidates, including the 27 from MF97.

Figure \ref{fig_diagnostic} shows an example for a small region $\sim$1.5\arcmin\ south of the nucleus containing two of the MF97 objects and several new SNR candidates. In this example we have combined the three star-subtracted emission line images into a single color panel that shows how the stronger \sii\ and/or \oiii\ emission from the SNR candidates makes them stand out.  The \sii:\ha\ ratio image was a key diagnostic for drawing our eyes to potential objects of interest. Then an assessment of the integrity of the candidate as an emission object was made by inspection of the actual images.  This was done to separate candidates from stellar residuals or false regions of higher ratio in the ratio map that were due to noise.

Having performed similar SNR searches in other galaxies such as M33 and M83, it is worth noting some differences for \gal.  M33 is of course much closer, and the nebulae of interest are almost always resolved.  M83 is much more distant (4.6 Mpc) than M33, but our search there was aided by the exceptional seeing conditions we obtained at the Magellan telescope (0.5\arcsec).  Many objects were resolved, but others extended down to the limits of what even HST could resolve ($\sim$1-2 pc).  Our WIYN survey of \gal\ did not have exceptional seeing, and the distance is some 50\% larger than for M83.  Hence, relatively few of the nebulae of interest are resolved, and with variations in the complex galaxy background, it is much more difficult to perform a systematic search.  The use of the \sii:\ha\ ratio image was particularly helpful for \gal, which is the most distant galaxy for which we have performed this kind of SNR survey. Nonetheless, while we have expanded the SNR candidate list very substantially, clearly completeness has not been achieved.  Our list of 147 SNR candidates falls far short of M83, for example, even though the SN rate is larger in \gal.  Higher resolution data (better seeing and/or HST imaging) would no doubt help substantially, but the greater distance is still a limiting factor.

In addition, we initially selected 51 objects with relatively high \oiii:\ha\ ratios (using an \oiii:\ha\ ratio image in the display), in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy. With ten SNe in the last century, one might expect a number of young, ejecta-dominated SNRs to be present.  Though none of the O-selected candidates had ratios as extreme as seen for Cas A or 1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.  The vast majority of these nebulae turned out to be \hii\ regions with somewhat enhanced ionization state, and so these form the bulk of the \hii\ sample we use for comparison below. Finally, we inspected the positions of the nine\footnote{As of the 2011 observations there were nine SNe; a tenth SN was recorded in 2017.} historical SNe in \gal\ for evidence of nebular emission; we only detected line emission at the positions of SN1980K and SN2004et, both of which we targeted for follow-up spectroscopy.

%\todo[inline]{ksl - It might be worthwhile to have a few sentences of comparison here to our work on M83 where the Magellan seeing made if far easier to see extended emission, and in M33 of course where all of the SNRs are resolved.  This is about the limit of what we can do from the ground, particularly with the seeing we had with WYIN.  To do better, one needs better seeing.  WPB: I tried to incorporate these points into the text added above with the exmaple diagnostic figure.}

@@

\todo[inline]{We need a consistent story about the HII regions.  We mention that we selected some O3 objects.  We got spectra of 24 of these.   We have another 41 spectra of HII regions along the slit.  We got very few HII regions just by chance, though these are included in the 41.  It's hard to actually parse out the history of which are which.  WPB: Note that I added some words above in the ``[O III] object" discussion to at least partially address this concern.}

@@

\begin{figure}
\plotone{fig_N6946_diagnostic.pdf}
\caption{This figure (placeholder) demonstrates the diagnostic process used to find SNR candidates in NGC~6946.  The region shown is 35\arcsec\ in the N-S dimension and is centered $\sim$1.5\arcmin\ south of the nucleus.  At upper left is a star-subtracted \sii\ image for reference.  At upper right, we show a color image of subtracted emission line images, where red is H$\alpha$, green is \sii, and blue is \oiii.  Bottom left shows the \sii:H$\alpha$ ratio image of the region, where elevated values of the  ratio are white and low values are black.  The lower right image shows the green continuum image, which is useful for identifying the presence of stellar subtraction residuals.  The red circles are 4\arcsec\ in diameter and show two MF objects and four newly identified SNR candidates from our survey.  Note the appearance in the ratio image, where most of the emission nebulae show low ratios, but the objects in the red circles stand out in the ratio.  The coloration differences in the upper right panel are due to relatively stronger \sii\ and/or \oiii\ emission from the SNR candidates compared with the photoionized gas. \label{fig_diagnostic}}
\end{figure}

\begin{figure}
\plotone{fig_example_spectra.pdf}
\caption{Examples of the spectra obtained for three representative SNR candidates and one \hii\ region.  The three SNR spectra were selected to illustrate the quality of the spectra for a bright, medium bright and fairly faint candidate.  \label{fig_spectra}}
\end{figure}

@@

\begin{figure}
\plottwo{fig_n2_ha_gc.pdf}{fig_s2_ha_gc.pdf}
\caption{Line ratios of [N II]:\ha\ and [S II]:\ha\ as a function of GCD.  Both SNR candidates and \hii\ regions are shown.     \label{fig_metal_ratios}}
